Anonymizing ids

### 2021-08-30 text/21/anonymizing-ids.Rmd
Added poisson-inference.md

```{r, echo=FALSE}
e <- data.frame(private_id=as.character(private_id), random_id=as.character(private_id+480035489))

e %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```

>>>>

```{r, echo=FALSE}
e <- data.frame(private_id=as.character(private_id), random_id=as.character(private_id+480035489))
e %>%
  kbl %>%
  kable_minimal(full_width=FALSE, position="left")
```
